### 2015-07-09 narrative/migration.tex
start to reshape the proposal
scott changes

\subsubsection{Migration}

@@

Sirocco groups like media into aggregated volumes on a service node, and like
service nodes with like media into pseudo-tiers. It accomplishes both using
attributes such as latency to first byte, bandwidth to and from the media, and
some function representing the resilience capabilities of the attached media.
In addition to these static attributes, when grouping servers into
pseudo-tiers, Sirocco also may employ more dynamic attributes such as CPU load
and the rate-of-change of the media use.

Grouping into pseudo-tiers is not a formal, nor rigid, concept within Sirocco,
at present. In classic HSM the tiering is often a formally expressed concept,
embodied both in the architecture and the implementation. In Sirocco, though,
it is not directly expressed. Instead, a client or server that attempts to make
a decision relative to migration and staging uses the attributes discussed
above to constrain the choice of candidates. For instance, a server acting as
an off-node writeback cache for a compute node might only have access to
volatile dynamic RAM for use as storage media and a client might deposit data
that is marked for persistent media as a resilience constraint. At some point,
then, such a server must copy or move the data to another Sirocco server with
media matching, or exceeding, the resilience constraint. At that point in time,
all servers managing appropriate persistent media are candidates but
second-order attributes, such as latency and bandwidth of a candidate's managed
media would tend to dominate the ranking. Thus, the concept of a ``tier''
becomes an artifact of decision rather than a formal concept.

>>>>

\subsection{Migration}

@@

Sirocco groups like media into aggregated volumes on a service node, and like
service nodes with like media into pseudo-tiers. It accomplishes both using
attributes such as latency to first byte, bandwidth to and from the media, and
some function representing the resilience capabilities of the attached media.
In addition to these static attributes, when grouping servers into
pseudo-tiers, Sirocco may also employ more dynamic attributes such as CPU load
and the rate-of-change of the media use.

Grouping into pseudo-tiers is not a formal, nor rigid, concept within Sirocco,
at present. In classic HSM the tiering is often a formally expressed concept,
embodied both in the architecture and the implementation. In Sirocco
it is not directly expressed; instead, a client or server that attempts to make
a decision relative to migration and staging uses the attributes discussed
above to constrain the choice of candidates. For instance, a server acting as
an off-node writeback cache for a compute node might only have access to
volatile dynamic RAM for use as storage media and a client might deposit data
that is marked for persistent media as a resilience constraint. At some point,
then, such a server must copy or move the data to another Sirocco server with
media matching, or exceeding, the resilience constraint. At that point in time,
all servers managing appropriate persistent media are candidates but
second-order attributes, such as latency and bandwidth of a candidate's managed
media would tend to dominate the ranking. Thus, the concept of a ``tier''
becomes an artifact of decision rather than a formal concept.
